Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-03-10 awipev-CO2.Rmd
rds rather than Rdata

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
load(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.Rdata"))
#load(file = paste0(path, "fb_server/shinyroot/AWIPEV-CO2/nydata_hour_shiny.Rdata"))
#load(file = "../fb_server/shinyroot/AWIPEV-CO2/nydata_shiny.Rdata") #d
# load = d_hour
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
         AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
         #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
         #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
         ) %>%
  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered,temp_insitu=Temp_SBE38_filtered, sal_fb=Salinity_filtered,temp_fb=Temperature_filtered)
```

@@

save(file= paste0(path, "fb_data/d_all.Rdata"), d_all)

@@

## Temperatures
Several temperature sensors are on site, 1 inside the Ferrybox and 2 outside:

@@

pdelta_at_snapo
pdelta_at_snapo_dygraph
p_at_ts
pdelta_ct_snapo
pdelta_ct_snapo_dygraph
p_ct_ts
ggsave(paste0("figures/delta_at_awipev_snapo.png"), pdelta_at_snapo, units="cm")
ggsave(paste0("figures/delta_ct_awipev_snapo.png"), pdelta_ct_snapo, units="cm")
```
```{r save all, echo=FALSE, message= FALSE, warning=FALSE}
# d_hour is the real data set that is read at the beginning of the script
# d_all comprises additional columns calculated in this script
# These additional variablrs are useful elsewhere (for example in "presentation")
# Hence, here we save it for this use
save(file= paste0(path, "fb_data/d_all.Rdata"), d_all)
```

>>>>

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.rds"))
# load = d_hour
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
         AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
         #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
         #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
         ) %>%
  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered,temp_insitu=Temp_SBE38_filtered, sal_fb=Salinity_filtered,temp_fb=Temperature_filtered)
```

@@

save(file= paste0(path, "fb_data/d_all.rds"), d_all)

@@

```{r water masses, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
# One tries to identify water masses coming from the Atlantic or freshwater

```
## Temperatures
Several temperature sensors are on site, 1 inside the Ferrybox and 2 outside:

@@

pdelta_at_snapo
pdelta_at_snapo_dygraph
p_at_ts
pdelta_ct_snapo
pdelta_ct_snapo_dygraph
p_ct_ts
ggsave(paste0("figures/delta_at_awipev_snapo.png"), pdelta_at_snapo, units="cm")
ggsave(paste0("figures/delta_ct_awipev_snapo.png"), pdelta_ct_snapo, units="cm")
```
```{r save all, echo=FALSE, message= FALSE, warning=FALSE}
# d_hour is the real data set that is read at the beginning of the script
# d_all comprises additional columns calculated in this script
# These additional variablrs are useful elsewhere (for example in "presentation")
# Hence, here we save it for this use
save(file= paste0(path, "fb_data/d_all.rds"), d_all)
```
